TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems

### 2017-04-07 ICESS2017/paper.tex
Add ICESS2017

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{
\IEEEauthorblockN{
Takuro Yamamoto\IEEEauthorrefmark{1},
Takuma Hara\IEEEauthorrefmark{2},
Takuya Ishikawa\IEEEauthorrefmark{2}, 
Hiroshi Oyama\IEEEauthorrefmark{3},
Hiroaki Takada\IEEEauthorrefmark{2} and
Takuya Azumi\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
\IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
}

@@

This section describes the system model of TINET+TECS, including basic technologies such as TINET and TECS.
A system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
TINET+TECS is a component-based TCP/IP protocol stack in which the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings using the TECS method.
Moreover, the TECS adapter supports the legacy codes for existing TCP/IP applications.

@@

\subsection{TINET+TECS}
TINET+TECS, the proposed componentized TCP/IP protocol stack, comprises a number of some TECS components.
This section describes the components of the TINET+TECS framework with the aid of component diagrams.
% In addition, TECS functionalities applied to the proposed system such as {\it send}/{\it receive} specifier and adapter are explained.

@@

TECS supports dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

@@

\subsection{TECS adapter}
\label{sec:TECS Adapter}

@@

Memory consumption of without and with dynamic connection is shown in Fig. \ref{fig:EvaluationOfDynamicConnection}.
The dynamic connection case consumes the more RAM memory because, as mentioned in Section \ref{sec:DynamicConnection}, call ports with {\it [dynamic]} are not optimized and allocated in RAM areas.
However, the overall memory consumption is lower under the proposed framework.

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

@@

Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}, lwIP \cite{par:lwIP}.

@@

This paper also presented dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
TINET+TECS utilizes dynamic connection to satisfy the TINET specification for supporting static generation of CEPs and REPs.
As the TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.

>>>>

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{
\IEEEauthorblockN{
Takuro Yamamoto\IEEEauthorrefmark{1},
Takuma Hara\IEEEauthorrefmark{2},
Takuya Ishikawa\IEEEauthorrefmark{2}, 
Hiroshi Oyama\IEEEauthorrefmark{3},
Hiroaki Takada\IEEEauthorrefmark{2}, and
Takuya Azumi\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
\IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
}

@@

This section describes the system model of TINET+TECS, including basic technologies such as TINET and TECS.
A system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
TINET+TECS is a component-based TCP/IP protocol stack in which the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components (Section \ref{sec:TINET+TECS}).
CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings using the TECS method (Section \ref{sec:DynamicConnection}).
Moreover, the TECS adapter supports the legacy codes for existing TCP/IP applications (Section \ref{sec:TECSAdapter}).

@@

\subsection{TINET+TECS}
\label{sec:TINET+TECS}

TINET+TECS, the proposed componentized TCP/IP protocol stack, comprises a number of some TECS components.
This section describes the components of the TINET+TECS framework with the aid of component diagrams.
% In addition, TECS functionalities applied to the proposed system such as {\it send}/{\it receive} specifier and adapter are explained.

@@

TECS supports dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

@@

\subsection{TECS adapter}
\label{sec:TECSAdapter}

@@

Memory consumption of without and with dynamic connection is shown in TABLE \ref{fig:EvaluationOfDynamicConnection}.
The dynamic connection case consumes the more RAM memory because, as mentioned in Section \ref{sec:DynamicConnection}, call ports with {\it [dynamic]} are not optimized and allocated in RAM areas.
However, the overall memory consumption is lower under the proposed framework.

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
    {\tabcolsep = 1mm
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    }
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

@@

Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP} and lwIP \cite{par:lwIP}.

@@

This paper also presented dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
TINET+TECS utilizes dynamic connection to satisfy the TINET specification for supporting static generation of CEPs and REPs.
As the TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.
TINET+TECS and application programs used in the evaluation are all open-source, and may be downloaded from our website \cite{url:TINET+TECS}.
